\EVOSUITE at the SBST 2020 Tool Competition

### 2020-03-25 papers/sbst20/main.tex
Fix.

\subsubsection*{GUAVA-212, GUAVA-22, PDFBOX-265, PDFBOX-278, PDFBOX-285,
PDFBOX-40, PDFBOX-91} The mutation analysis failed due to a
\texttt{java.util.concurrent.ExecutionException} thrown by the experimental
infrastructure.

%% PDFBOX-62 1.2% coverage 0% mutation score

\subsubsection*{PDFBOX-62} \EVOSUITE crashed due to some Mocking stuff.

>>>>

\subsubsection*{GUAVA-212, GUAVA-22, PDFBOX-265, PDFBOX-278, PDFBOX-285,
PDFBOX-40, PDFBOX-91, PDFBOX-62} The mutation analysis failed due to a
\texttt{java.util.concurrent.ExecutionException} thrown by the experimental
infrastructure.

%% PDFBOX-235 0% coverage 0% mutation score

\subsubsection*{PDFBOX-235} \EVOSUITE crashed due to some Mocking stuff.
